---
title: "ODD ASS P2"
author: "Murat Orhan"
date: "25 Kasım 2018"
output: html_document
---

```{r}
## Load tidyverse
library(tidyverse)
```

```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(scales)
```

## Getting the .rds file
Below the rds file is downloaded from github to a local data frame (raw_data) and refined for analysis

```{r}
#download from github 
raw_data <- readRDS("C:/Users/Murat/Desktop/BIG DATA YL/BDA 503 DATA ANALYTICS(R)/W4/car_data_aggregate.rds")

head(raw_data)
```

```{r}
tail(raw_data)
```

## Making some correction on data
```{r cars}
#raw_data$brand_name <- str_replace(raw_data$brand_name,"ASTON MARTÄ°N","ASTON MARTIN") ## correction on strings

dim(raw_data) # find out the index of latest row number
```

## Deleting the last row because of total value
```{r}
raw_data <- raw_data %>% slice(-c(1490))
tail(raw_data)
```

## Removing dublicated brand names 
```{r}
raw_data %>%  
filter(total_total>0 & comm_total>0) %>%
distinct(sort(brand_name))
```

## Showing annual total sales amount of cars sorted by the most sold brand 
```{r}
raw_data %>% group_by(brand_name,year) %>% summarise(totalsales = sum(total_total)) %>% arrange(desc(totalsales))
```

## Let's get some visualization

Comparing total annual automobile sales of BMW and AUDI;
```{r}
raw_data %>%
  group_by(brand_name, year) %>% 
  filter(brand_name %in% c("BMW", "AUDI")) %>%
  summarize(yearly_auto_total = sum(auto_total))%>%
  ggplot(data=., aes(x=year, y=yearly_auto_total, fill=brand_name)) +
  geom_bar(stat="identity", position=position_dodge())+
  labs(x="Years", y = "Number Of Sales", fill="Brands") +
  theme_minimal()
```

Showing which brand sold at most in Turkey between 2016 and 2018
```{r}
summary <- raw_data %>% group_by(brand_name) %>% summarize(total_total=sum(total_total))
   
ggplot(summary,aes(x=reorder(brand_name,total_total),y=total_total))+
coord_flip()+
geom_col(fill="blue")+
theme_bw()+
theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank(),text = element_text(size=14), axis.text.y=element_text(size=10))+
scale_y_continuous(labels=comma)
```

