---
title: "ODD ASS P2"
author: "Murat Orhan"
date: "25 Kasım 2018"
output: html_document
---

```{r}
## Load tidyverse
library(tidyverse)
```

```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(scales)
```

## Getting the .rds file
Below the rds file is downloaded from github to a local data frame (raw_data) and refined for analysis

```{r}
#download from github 
raw_data <- readRDS("C:/Users/Murat/Desktop/BIG DATA YL/BDA 503 DATA ANALYTICS(R)/W4/car_data_aggregate.rds")

head(raw_data)
```

```{r}
tail(raw_data)
```

## Making some correction on data
```{r cars}
raw_data$brand_name = str_replace(raw_data$brand_name, "MARTIN", "MARTIN")

dim(raw_data) # find out the index of latest row number
```

## Deleting the last row because of total value
```{r}
raw_data <- raw_data %>% slice(-c(1490))
tail(raw_data)
```

## Removing dublicated brand names 
```{r}
raw_data %>%  
filter(total_total>0 & comm_total>0) %>%
distinct(sort(brand_name))
```

## Showing annual total sales amount of cars sorted by the most sold brand 
```{r}
raw_data %>% group_by(brand_name,year) %>% summarise(totalsales = sum(total_total)) %>% arrange(desc(totalsales))
```

## Let's get some visualization

Comparing total annual automobile sales of BMW and AUDI;
```{r}
raw_data %>%
  group_by(brand_name, year) %>% 
  filter(brand_name %in% c("BMW", "AUDI")) %>%
  summarize(yearly_auto_total = sum(auto_total))%>%
  ggplot(data=., aes(x=year, y=yearly_auto_total, fill=brand_name)) +
  geom_bar(stat="identity", position=position_dodge())+
  labs(x="Years", y = "Number Of Sales", fill="Brands") +
  theme_minimal()
```

Top 4 Car Sales per Brand in 2016
```{r}
raw_data %>% 
    filter(auto_total > 0 & comm_total > 0) %>%
    select(brand_name,auto_total,comm_total,total_total,year) %>%
    arrange(desc(year),desc(total_total)) %>%
    filter(year == "2016") %>%  
    group_by(brand_name) %>%
    summarize(year_total = sum(total_total)) %>%
    arrange(desc(year_total)) %>%
    top_n(4) %>% 
    mutate(prop=percent(year_total / sum(year_total))) %>%
    ggplot(data = ., aes(x="", y=prop, fill=brand_name))+ labs(x = "", y = "", title = "Top 4 Car Sales per Brand in 2016") + 
    geom_bar(width = 1, stat = "identity") + coord_polar("y", start=0) +
    theme(plot.title=element_text(hjust=0.5,face='bold',size=18)) +  
    theme_classic() + theme(axis.line = element_blank(), axis.text = element_blank(), axis.ticks = element_blank()) +       geom_text(aes(label=prop),position=position_stack(vjust = 0.5)) + guides(fill=guide_legend(title="Brand Name"))

```

